Aa Language Reference Manual

### 2019-04-29 v2/Ahir-asm/devel/docs/AaLRM.tex
Guards for function call expressions were not being printed.

@@

For convenience, there are some synthetic operations which
you can use to simplify coding an Aa program.  These
are listed below
\begin{itemize}
\item The \$reduce operation:
\begin{verbatim}
($reduce |  a  b  c)   
    (note: this is the same as  ((a+b)+c))
\end{verbatim}
Any associative operation may be used instead
of the or (add, mul, xor, and).
\item The \$split operation:  Suppose you want
to split a 32 bit variable into two 8-bit variables
and four 4-bit variables.  This can be done using
\begin{verbatim}
($split X 8 8 4 4 4 4) (a8 b8 c4 d4 e4 f4)
   (note: a8 := ($slice X 31 24) etc..)
\end{verbatim}
\item The \$concat operation:  This is the
reverse of a \$split.  
\begin{verbatim}
Y := ($concat a8 b8 c4 d4 e4 f4)
  (note: Y := (a8 && (b8 && (c4 && d4 ....))
\end{verbatim}
\item The \$excmux operations:  A multiplexor
whose selects are expected to be mutually exclusive.
\begin{verbatim}
Y := ($excmux s0 X0 s1 X1 s2 X2)
\end{verbatim}
This is equivalent to 
\begin{verbatim}
Y := ($reduce |
           ($mux s0 X0 0)
           ($mux s1 X1 0)
           ($mux s2 X2 0))
\end{verbatim}
Note that if all of s0,s1,s2 are 0, then
Y is assigned to 0.
\item The \$prioritymux operations:  A multiplexor
whose selects may not be mutually exclusive.
\begin{verbatim}
Y := ($prioritymux s0 X0 s1 X1 s2 X2
                $default 1)
\end{verbatim}
This is equivalent to 
\begin{verbatim}
Y := ($mux s0 X0
           ($mux s1 X1
                $mux s2 X2 1))
\end{verbatim}
\end{itemize}

>>>>

\subsection{A synthetic statement: the \$split statement}

Often, we need to split a large vector into several pieces.
Suppose you want
to split a 32 bit variable into two 8-bit variables
and four 4-bit variables.  This can be done using
\begin{verbatim}
$split (X 8 8 4 4 4 4) (a8 b8 c4 d4 e4 f4)
\end{verbatim}
This is actually translated to the following
sequence of assignment statements.
\begin{verbatim}
a8 := ($slice X 31 24)
a7 := ($slice X 23 16)
c4 := ($slice X 15 12)
...
f4 := ($slice X 3 0)
\end{verbatim}

@@

For convenience, there are some synthetic operations which
you can use to simplify coding an Aa program.  These
are listed below
\begin{itemize}
\item The \$reduce operation:
\begin{verbatim}
($reduce |  a  b  c)   
    (note: this is the same as  ((a+b)+c))
\end{verbatim}
Any associative operation may be used instead
of the or (add, mul, xor, and).
\item The \$concat operation:  This is the
reverse of a \$split.  
\begin{verbatim}
Y := ($concat a8 b8 c4 d4 e4 f4)
  (note: Y := (a8 && (b8 && (c4 && d4 ....))
\end{verbatim}
\item The \$excmux operations:  A multiplexor
whose selects are expected to be mutually exclusive.
\begin{verbatim}
Y := ($excmux s0 X0 s1 X1 s2 X2)
\end{verbatim}
This is equivalent to 
\begin{verbatim}
Y := ($reduce |
           ($mux s0 X0 0)
           ($mux s1 X1 0)
           ($mux s2 X2 0))
\end{verbatim}
Note that if all of s0,s1,s2 are 0, then
Y is assigned to 0.
\item The \$prioritymux operations:  A multiplexor
whose selects may not be mutually exclusive.
\begin{verbatim}
Y := ($prioritymux s0 X0 s1 X1 s2 X2
                $default 1)
\end{verbatim}
This is equivalent to 
\begin{verbatim}
Y := ($mux s0 X0
           ($mux s1 X1
                $mux s2 X2 1))
\end{verbatim}
\end{itemize}
